%% Cheng-Shun (Ryan) Chuang — CV / PhD Application Resume
%% Compile with: pdflatex resume.tex
\documentclass[10pt,letterpaper]{article}

%% ── Packages ─────────────────────────────────────────────────────────────────
\usepackage[margin=0.50in, top=0.36in, bottom=0.36in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{array}
\usepackage{setspace}
\input{glyphtounicode}
\pdfgentounicode=1

%% ── Colors ───────────────────────────────────────────────────────────────────
\definecolor{accent}{HTML}{2563EB}
\definecolor{muted}{HTML}{6B7280}

%% ── Typography ───────────────────────────────────────────────────────────────
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setstretch{0.96}
\setlength{\emergencystretch}{3em}
\sloppy

%% Section headings
\titleformat{\section}
  {\normalsize\bfseries\color{accent}}
  {}{0em}{\MakeUppercase}
  [\color{accent}\titlerule]
\titlespacing{\section}{0pt}{4pt}{1pt}

%% ── Helpers ──────────────────────────────────────────────────────────────────
\newcommand{\resumeItem}[1]{\item\small #1}

\newcommand{\entryHeader}[4]{%
  \noindent\textbf{#1} \textit{\small\color{muted}#2}\hfill \textit{\small\color{muted}#3}\\
  {\small #4}
  \vspace{1pt}
}

\newcommand{\entryHeaderSingle}[3]{%
  \noindent\textbf{#1}\hfill \textit{\small\color{muted}#2}\\
  {\small\textit{\color{muted}#3}}
  \vspace{1pt}
}

\newcommand{\skillLine}[2]{\small\textbf{#1:} #2\\[1pt]}

%% ── Document ─────────────────────────────────────────────────────────────────
\begin{document}

%% ── Header ───────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries CHUANG, CHENG-SHUN (RYAN)}\\[5pt]
  \small
  \href{mailto:ryan70235@gmail.com}{ryan70235@gmail.com}
  \enspace\textbullet\enspace
  +1\,(571)\,331-6196
  \enspace\textbullet\enspace
  \href{https://ulrixon.github.io}{ulrixon.github.io}
  \enspace\textbullet\enspace
  \href{https://github.com/Ulrixon}{github.com/Ulrixon}
\end{center}
\vspace{2pt}

%% ── Summary ──────────────────────────────────────────────────────────────────
\section{Professional Summary}

{\small Computer Science M.Eng.\ student and Graduate Research Assistant focused on health AI, computer vision, full-stack research platforms, and cloud deployment. Experience building research software with React, TypeScript, Python, Flask/FastAPI, PostgreSQL, SQLAlchemy, PyTorch, AWS, GCP, Docker, Terraform, and GitHub Actions.}
\vspace{1pt}

%% ── Education ────────────────────────────────────────────────────────────────
\section{Education}

\entryHeader{Virginia Tech}{\ ·\ Alexandria, VA, USA}
            {Jan.~2025 -- Jan.~2027 (Expected)}
            {Master of Engineering in Computer Science}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=1pt]
  \resumeItem{GPA: 4.0/4.0}
  \resumeItem{Relevant coursework: Machine Learning, NLP, AI Tools for Software Engineering, Advanced Topics in Data \& Information Systems, Advanced Topics in Systems, Verification \& Validation of Scientific Computing, Research \& Thesis}
\end{itemize}
\vspace{1pt}

\entryHeader{National Taipei University (NTPU)}{\ ·\ New Taipei City, Taiwan}
            {Sep.~2019 -- June~2024}
            {Bachelor of Arts in Economics}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=1pt]
  \resumeItem{Overall GPA: 3.95/4.0 \,|\, Last 60 credits: 4.0/4.0 \,|\, CS Courses: 4.0/4.0}
  \resumeItem{Coursework: OS, Databases, ANN \& Deep Learning, Computer Vision}
  \resumeItem{Awards: Academic Excellence (3$\times$), Falcon Award, Dean's Award}
\end{itemize}
%% ── Publications ─────────────────────────────────────────────────────────────
\section{Publications}

\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=1pt]
  \resumeItem{Cusati, J., \textbf{Chuang, C.-S.}\ \textbf{Virginia Tech Transportation Safety Index (VTTSI).}
    \textit{\href{https://arxiv.org/abs/2606.21154}{arXiv:2606.21154 [cs.CY]}}, 2026.
    [\textit{Second Author}]
    Proposed a real-time, cloud-native transportation safety index combining connected-vehicle telemetry,
    Empirical Bayes crash stabilization, and CRITIC-weighted MCDM scoring.}

  \resumeItem{\textbf{Chuang, C.-S.}\ et al.\ \textbf{Impact of Linear Dimensionality Reduction on Machine Learning
    Performance: A Case Study on Fashion-MNIST.}
    \textit{Computing Conference 2026}, In Press.
    [\textit{Main Author}]
    Evaluated how PCA, LDA, Factor Analysis, and Random Forest feature selection affect downstream classifiers;
    SVM+PCA achieved top accuracy of 0.8995.}

  \resumeItem{[Co-Author] \textbf{Design of a Low-Cost, High-Resolution Underwater Acoustic Imager with
    Integrated Deep Learning Enhancement.}
    \textit{IEEE Sensors Journal}, 2025.
    Integrated a lightweight U-Net (${\sim}$1M params) achieving 7--9$\times$ axial and
    2--3$\times$ lateral resolution improvement over baseline ASAI.}
\end{itemize}

%% ── Research Projects ────────────────────────────────────────────────────────
\section{Research Projects}

\entryHeaderSingle{Virginia Tech Transportation Safety Index (VTTSI)}{Sep.~2025 -- Dec.~2025}
                  {Python · Empirical Bayes · MCDM (CRITIC/SAW/EDAS/CODAS) · FastAPI · Streamlit · GCP}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=1pt]
  \resumeItem{Developed a real-time road safety scoring system (0--100) integrating VDOT crash history
    with connected-vehicle telemetry at 15-minute resolution.}
  \resumeItem{Published the framework as an arXiv preprint:
    \href{https://arxiv.org/abs/2606.21154}{arXiv:2606.21154}.}
  \resumeItem{Applied Empirical Bayes crash modeling with uplift factors (speed deficit, VRU conflicts)
    and a CRITIC-weighted hybrid MCDM framework (SAW--EDAS--CODAS) for multi-criteria ranking.}
\end{itemize}
\vspace{1pt}

\entryHeaderSingle{Taiwanese Car Plate Recognition}{May~2023 -- June~2023}
                  {Python · YOLOv8 · Computer Vision · Object Detection}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=1pt]
  \resumeItem{Trained YOLOv8 models to recognize Taiwanese license plates from moving-vehicle video;
    achieved \textbf{mAP@IoU\,=\,0.5 of 0.986} (detection) and 0.966 (OCR), with zero errors in
    static parking-lot scenarios.}
\end{itemize}

%% ── Experience ───────────────────────────────────────────────────────────────
\section{Experience}

\entryHeaderSingle{Graduate Research Assistant --- ResonaCare Surgical Video Rating Platform}{May~2026 -- Present}
                  {Virginia Tech}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=1pt]
  \resumeItem{Building ResonaCare, a React/TypeScript and Flask/PostgreSQL platform for surgical-video rating research with rater, researcher, and admin workflows.}
  \resumeItem{Implemented assignment-scoped 3--30s segment annotation, six-dimension OSATS category ratings, comment review/invalidation, CSV exports, and consent-gated study-event logging.}
  \resumeItem{Integrated AWS deployment and AI evidence paths: S3 media upload, Amplify/Lambda/RDS stack, Bedrock voice classification, SageMaker/ResNet-18 frame analysis, and GitHub Actions CD.}
\end{itemize}
\vspace{1pt}

\entryHeaderSingle{TVBS News --- QA Engineer Intern}{Jan.~2024 -- June~2024}
                  {Taipei, Taiwan}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=1pt]
  \resumeItem{Ensured mobile app quality through systematic bug identification and regression testing.}
  \resumeItem{Built and tested RESTful APIs using MVC architecture, improving data retrieval speed and stability.}
\end{itemize}
%% ── Technical Skills ─────────────────────────────────────────────────────────
\section{Technical Skills}

\skillLine{Languages}{Python, TypeScript, JavaScript, C++, SQL}
\skillLine{Machine Learning and Deep Learning}{PyTorch, TensorFlow, Keras, scikit-learn, YOLOv8, U-Net, ResNet-18}
\skillLine{Software Engineering}{React, Flask, FastAPI, SQLAlchemy, Docker, Terraform, GitHub Actions, Linux, WSL2}
\skillLine{Cloud and Databases}{AWS Amplify, AWS Lambda, Amazon RDS, Amazon S3, Amazon SageMaker, Amazon Bedrock, GCP, PostgreSQL, MySQL, Cloud SQL}

\end{document}
